\Title

### 2022-09-27 Grimaldi-etal-BiolCybernetics.tex
Introduction: 1.2

The challenges are numerous in such situations and two major obstacles must be highlighted: the computational delay and the energy budget. First, most existing solutions are built incrementally from models built to process low definition images, such as Le Net for MNIST (Le Cun, 98), to high definition images, such as VGG on Imagenet (VGG16). This has a cost and notably the fact that the computation time increases with the size of the image. This phenomenon has been mitigated by the increase in available computing power, notably thanks to the parallel processing implemented in GPU cards. However, the transition from images to videos, then to multiple cameras implies a further change of scale in the amount of data processed. It also raises an issue that is often not addressed when it comes to image categorization. Indeed, in autonomous driving, an important task is to react as quickly as possible to a possible collision, for example when a pedestrian crosses the street. As such, future systems should always be able to give a response at any time, instead of having to wait for the pipeline to provide the correct response. This online processing is also a feature of processing in biological systems and could be an important first contribution if we could translate these principles into future automated processes. 
Second, a major constraint for future systems is energy cost. As we have seen, fast computation time has been maintained for high-dimensional images, but at the cost of higher energy consumption. In addition, the need to solve increasingly complex tasks has required the construction of increasingly complex and deep architectures. As an example, the best performing model in the Imagenet challenge uses billions of parameters that typically cost 1Wh to train and about 1Wh to infer a single image. Less power-hungry solutions have emerged, such as Mobile Net, but they are not yet ready for practical use in autonomous cars, as the additional power consumption would be about 300W, or 20\% of the energy of an electric car under standard conditions.
Neuroscience could provide revolutionary answers to these two closely related problems. Indeed, the human brain has the remarkable property of being able to react at any time, while consuming a reasonable amount of energy, estimated at 5W at rest. This system is the result of millions of years of natural selection, and a striking difference between biological neural networks and artificial ones is the representation they use. CNNs, for example, represent information passing from one layer to another as tensors representing visual information densely over the visual topography, while representing different properties in different channels. On the other hand, information in a large majority of biological neural networks is represented as spikes, i.e. prototypical all-or-nothing events whose only parameters are their timing and the address of the neuron that emitted this spike. Why spikes? It is not yet known why most biological systems have evolved to use this representation, but one major advantage seems to be some form of efficiency. In the human brain, each of the approximately ten trillion nerve cells emits on average one spike per second, but each neuron fires with great variability, and up to 300 spikes per second. Many attempts have been made to build artificial spiking neural networks, and in particular to achieve the same performance as observed in classical CNNs, but with a lower energy budget. However, none of these networks has yet surpassed the state of the art performances. Here, we will try to focus on a property of spike neurons inspired by neurobiology to progress in this direction.
\subsection{What can neuroscience bring to computer vision?}% and the Hetero-synaptic delays in spiking neurons}
% 1.2.a
Let's focus first on some existing spiking neural network models. one first motivation for these models was to understand the biological observations at different scales. For instance the Hodgkin Huxley mode describes the 'dynamic of the membrane potential and the role of the different voltage-gated ion channels. It also explains how the all may emit a spike. Larger scale models introduce an explicit spiking mechanism, for instance in the Integrate-and-Fine model which allows to predict the emerging states of a network of recurrently connected neurons (Brunel). Several models have sealed up the system to include more neurons such as the Virtual Brain (Sanz) which allows to mix spiking neural nets with analog neural mass models. However these methods are merely descriptive and have application in neuroscience and few have had an impact in computer vision.

Another class of attempts have designed spiking neural networks that aim to have applications in machine learning. One of these is the Spike Nap algorithm which uses a radical approach by anding information using one spite per nen non :(Delorme). Another branch of spiking neural networks attempt to determine the structure of the network such as to minimize a cot function. This has been implemented in the Spike Prop algorithm (Bonte) and is now widely used in methods Trying to transfer the performance of CNN s to Sn Ns, for instance by using a surrogate gradient approach. However, the performance of SNN always fall short of that of analog networks and the question of the advantage of using spin is still open. A novel generation of algorithms has emerged with so-called silicon retina which mimi de the output of the retina, by representing the information using espibes. one of this approach is that of Lagorce, which uses the time to the last spike to encode information in in so-called temporal surfaces. We have recently extended this Mots algorithm to provide with an online response and shown near-son - performances on categwitha notable more energy-efficient budget. A naige of similar algorithms are applied to real-life applications like optic flow (Benotman), depth estimation (Dandelot) on Gesture-Recently such algorithm was used in the space industry which is famous for its stringeant selection process.

>>>>

The challenges are numerous in such situations and two major obstacles must be highlighted: the computational delay and the energy budget. First, most existing solutions are built incrementally from models built to process low definition images, such as Le Net for MNIST (Le Cun, 98), to high definition images, such as VGG on Imagenet (VGG16). This has a cost and notably the fact that the computation time increases with the size of the image. This phenomenon has been mitigated by the increase in available computing power, notably thanks to the parallel processing implemented in GPU cards. However, the transition from images to videos, then to multiple cameras implies a further change of scale in the amount of data processed. It also raises an issue that is often not addressed when it comes to image categorization. Indeed, in autonomous driving, an important task is to react as quickly as possible to a possible collision, for example when a pedestrian crosses the street. As such, future systems should always be able to give a response at any time, instead of having to wait for the pipeline to provide the correct response. This online processing is also a feature of processing in biological systems and could be an important first contribution if we could translate these principles into future automated processes. 
Second, a major constraint for future systems is energy cost. As we have seen, fast computation time has been maintained for high-dimensional images, but at the cost of higher energy consumption. In addition, the need to solve increasingly complex tasks has required the construction of increasingly complex and deep architectures. As an example, the best performing model in the Imagenet challenge uses billions of parameters that typically cost 1Wh to train and about 1Wh to infer a single image. Less power-hungry solutions have emerged, such as Mobile Net, but they are not yet ready for practical use in autonomous cars, as the additional power consumption would be about 300W, or 20\% of the energy of an electric car under standard conditions.

Neuroscience could provide revolutionary answers to these two closely related problems. Indeed, the human brain has the remarkable property of being able to react at any time, while consuming a reasonable amount of energy, estimated at 5W at rest. This system is the result of millions of years of natural selection, and a striking difference between biological neural networks and artificial ones is the representation they use. CNNs, for example, represent information passing from one layer to another as tensors representing visual information densely over the visual topography, while representing different properties in different channels. On the other hand, information in a large majority of biological neural networks is represented as spikes, i.e. prototypical all-or-nothing events whose only parameters are their timing and the address of the neuron that emitted this spike. Why spikes? It is not yet known why most biological systems have evolved to use this representation, but one major advantage seems to be some form of efficiency. In the human brain, each of the approximately ten trillion nerve cells emits on average one spike per second, but each neuron fires with great variability, and up to 300 spikes per second. Many attempts have been made to build artificial spiking neural networks, and in particular to achieve the same performance as observed in classical CNNs, but with a lower energy budget. However, none of these networks has yet surpassed the state of the art performances. Here, we will try to focus on a property of spike neurons inspired by neurobiology to progress in this direction.
%
\subsection{What can neuroscience bring to computer vision?}% and the Hetero-synaptic delays in spiking neurons}
%%%-----------------------------------------------------------------
Let us first focus on some existing spiking neural network models. A first motivation for these models was to understand biological observations at different scales. For example, the Hodgkin-Huxley model describes the dynamics of the membrane potential and the role of different voltage-dependent ion channels. It also explains how the model can produce a spike. Larger scale models introduce an explicit spiking mechanism, for example in the Integrate-and-Fire model. It predicts the emergent states of a recurrently connected neural network (Brunel). Several models have increased the scale of the system to include more neurons, such as the Virtual Brain (Sanz), which mixes spike neural networks with analog neural mass models. However, these methods are mainly descriptive with applications in neuroscience but few have had an application in computer vision.

Another class of approaches have designed spiking neural networks that aim to have applications in machine learning. One of these is the SpikeNet algorithm which uses a radical approach by encoding information using one spike per neuron (Delorme). Another type of spiking neural network attempts to determine the structure of the network in order to minimize a cost function. This was implemented in the SpikeProp algorithm (Bohte) and is now widely used in methods that attempt to transfer performance from CNNs to SNNs, for example using a surrogate gradient approach. However, the performance of SNNs is still lower than that of analog networks and the question of the advantage of using spikes remains open. A new generation of algorithms has emerged with the advent of the so-called silicon retina, which mimics the output of the retina by representing information using spikes. One such approach is that of Lagorce, which uses the time to the last spike to encode information into so-called temporal surfaces. We have recently extended this HOTS algorithm to provide an online response and have shown performance close to that of SOTA for categorization, with a much more efficient energy budget. A series of similar algorithms are applied to real-life applications such as optical flow (Benosman), depth estimation (Dardelet), or gesture recognition (Marro). Recently, such an algorithm has been used in the space industry which is famous for its stringent selection process.
